---
title: "Market Basket Analysis"
author: "Abhishek Unni Krishnan"
date: 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r}

library(arules)
library(plyr)
library(dplyr)
library(readxl)
library(arulesViz)


```

*Problem Statement:Finding the best item's to bundle for promotion with the items Pasta Sauce due to surplus inventory*
*Part 1: Reading data from the transaction file:*
```{r}
setwd("C:\\Users\\abhit\\OneDrive\\Documents\\Uni\\Marketing analytics")
Transaction_1 = read.transactions("Market_Basket_Optimisation.csv", format = 'basket', sep = ',')

summary(Transaction_1)
```
*Part 2: Finding Top combinations in the transaction data*
```{r}
rules<-apriori(Transaction_1,parameter = list(support = .01, conf = .4, maxlen = 3))
summary(rules)
inspect(rules)
inspect(rules[1:10])
inspect(sort(rules, by = 'lift')[1:10])
print(rules)
```
*Part 3: Finding best combination with the Product Pasta sauce *
```{r}
rules<-apriori(Transaction_1,parameter = list(support = 0.1, conf = .05, maxlen = 2),
               appearance = list(lhs="pasta", default = "rhs")) #finding products purchases with pasta sauce
inspect(rules)
```
*Part 4: Inference*
*Based on the results above we can clearly see that along with pasta s sauce mineral water, spaghetti and eggs are usually bought together. We can ignore mineral water as that is a common purchase so we can not confidently say that there is a relationship between pasta sauce and mineral water so we choose the next two options that is spaghetti and eggs.*  

